Low Complexity Adaptive Beamformer\\ for Active Sonar Imaging

### 2015-08-13 LCAforActiveSonarImaging/lca.tex
la2pdf commit - 2015:08:13	16:47:15	(Thu13.Aug)

In this work we investigate a few questions related to the LCA that remain unanswered. One is what window function we can use, and how many windows we will need. We limit our study to the use of variations of the Kaiser-Harris window, since we observed neglible performance difference to using this function or any of the common trigonometric ones. The Kaiser windows are easy to compute, is fairly insensitive to coefficient errors, and can create windows with shapes spanning from rectangular to Gaussian. windows are needed, and what variations of the windows are necessary?

@@

ne is what window functions LCA should be allowed to choose from. This hardly seems to matter,   Our studies show minimal difference between the traditional windows, so the common and reasonable Kaiser-Harris window where the compromize between What windows should the LCA be allowed to choose from? How many is needed?  by Synnev\aa{}g demonstrated the potential of LCA,

>>>>

Synnev\aa{}g used a window set comprised of rectangular, Kaiser and inverted Kaiser functions. Of these only a specific Kaiser window were steered We limit our study to the use of variations of the parametric Kaiser-Harris window, since we observed neglible performance difference to using this function or any of the common trigonometric ones. The Kaiser windows are easy to compute, is fairly insensitive to coefficient inaccuracies, and can create windows with shapes spanning from rectangular to Gaussian.

In this work we investigate a few questions related to the LCA that remain unanswered. One is what window function we can use, and how many windows we will need.

@@
